Supporting Information : Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology

### 2019-03-16 SuppMat.Rmd
modified Verhulst with K=1

numsims<-10000
numsteps<-25
numlocs<-5
p0<-1

@@

for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-r
    ext_thrs<-p0/10

@@

# For global dispersal in D matrix 
res_verhulst_global<-c()
for(r in rlist){
    params<-r
    ext_thrs<-p0/10

@@

```{r fig_verhulst_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

```{r fig_verhulst_extrisk_d0_scl_0.6, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
verhulst_extrisk_d0<-readRDS(paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

@@

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Verhulst",paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_verhulst_global
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

@@

dt2<-tibble("Density dependence $(\\lambda_t^{i})$ with noise $(\\epsilon_t^{i})$" = c("$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} \\exp[r (1-P_t^{i}/K)$]",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} r/(1+aP_t^{i})^b$",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} r/[1+(aP_t^{i})^b]$",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} r/[1+\\exp \\{-a(1-P_t^{i}/b)\\}]$",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} [1+r(1-P_t^{i})]$",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} [1+r(K-P_t^{i})\\{1-\\exp(-sP_t^{i})\\}]$"
))

dt3<-tibble("\\hspace{-0.1 cm} Parameters used" = c("K = 50, sd = 1",
                            "a = 0.5, b = 100, sd = 1",
                            "a = 0.5, b = 4, sd = 0.8",
                           "a = 0.1, b= 0.1, sd = 1",
                           "sd = 0.6",
                           "s = 0.2, K = 50, sd = 0.6"
))

dt4<-tibble("$P_e^{i}$" = c("K",
                        "$(r^{1/b}-1)/a$",
                        "$[(r-1)^{1/b}]/a$",
                        "$[b\\{a+ln(r-1)\\}]/a$",
                        "1",
                        "K"
))

@@

<!--
# Vital rates in a stochastic age-structured model having specific tail-dependence \label{age_str_vitalrates}
A $N \times 2$ matrix, M, was generated for each of the left (Clayton, Survival Gumbel) and right 
(Survival Clayton, Gumbel) tail-dependent bivariate copulas, where $N = numsteps(=25) \times numsims(=10000)$.
We kept the same Kendall's correlation ($\tau = 0.6$) for each bivariate copula which used parameter accordingly
(see `iTau` function from `copula` package).-->

>>>>

numsims<-10000
numsteps<-25
numlocs<-5
K<-1
p0<-K
ext_thrs<-p0/10

@@

for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-c(r,K)

@@

# For global dispersal in D matrix 
res_verhulst_global<-c()
for(r in rlist){
    params<-c(r,K)

@@

```{r fig_verhulst_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}

pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

```{r fig_verhulst_extrisk_d0_scl_0.6, echo=F,results="hide"}

set.seed(seed)
numsims<-10000
verhulst_extrisk_d0<-readRDS(paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

@@

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Verhulst",paste0("K =1, sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(K = 1, sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(paste("(K = 1, sd = 0.6)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
x<-res_verhulst_global
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist)

@@

dt2<-tibble("Density dependence $(\\lambda_t^{i})$ with noise $(\\epsilon_t^{i})$" = c("$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} \\exp[r (1-P_t^{i}/K)$]",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} r/(1+aP_t^{i})^b$",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} r/[1+(aP_t^{i})^b]$",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} r/[1+\\exp \\{-a(1-P_t^{i}/b)\\}]$",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} [1+r(1-P_t^{i}/K)]$",
                          "$\\exp(\\epsilon_t^{i}) \\hspace{0.1 cm} [1+r(K-P_t^{i})\\{1-\\exp(-sP_t^{i})\\}]$"
))

dt3<-tibble("\\hspace{-0.1 cm} Parameters used" = c("K = 50, sd = 1",
                            "a = 0.5, b = 100, sd = 1",
                            "a = 0.5, b = 4, sd = 0.8",
                           "a = 0.1, b= 0.1, sd = 1",
                           "K = 1, sd = 0.6",
                           "s = 0.2, K = 50, sd = 0.6"
))

dt4<-tibble("$P_e^{i}$" = c("K",
                        "$(r^{1/b}-1)/a$",
                        "$[(r-1)^{1/b}]/a$",
                        "$[b\\{a+ln(r-1)\\}]/a$",
                        "K",
                        "K"
))

@@
